Adopting agile in the large: motivations, success factors and challenges

### 2014-05-03 journal/article.tex
Managers' roles

>>>>

\subsubsection{Agile is found to be hard}

A challenge many organizations came across was that an agile model was not
straight forward to implement.

A common problem in the agile implementations was the role of managers.
Especially the role of middle management was seen as unclear in agile
methods, but a cultural change would still be required on that level [P2].
It was described that people in management positions needed to resist the
tendency to take command and control to allow room for self-organization, but
the change in role was difficult to achieve for the people involved [P11, P52].
Nielsen and McMunn [P30] describe how the project management group had
previously worked through big up front plans and competing of resources, but
those ways would need to dramatically change.

Several other problems related to management roles were also presented. For
instance, Spayd [P49] describes how managers were left outside the roles offered
by the new agile model. In another case when Scrum masters were appointed from
the ranks of managers developers felt being micromanaged because of vague
understanding of the agile method [P27]. It was also described how mixing the
role of project manager and Scrum master created a conflict in interest, and
turned the Scrum manager's role into one of policing the team instead of
supporting the team [P30]. In some cases problems with manager positions were
solved by phasing out roles relating to the old model, and replacing them with
new positions more suitable for agile [P38, P52].
